My english activity log

### 2019-11-03 english-activity.Rmd
jusqu'au 03/11/2019

>>>>

29/10/2019 : I watched a video about mutations https://www.youtube.com/watch?v=vl6Vlf2thvI.

01/11/2019 : I watched a video about microscope drawings https://www.youtube.com/watch?v=NLKZ95aHqE4.

02/11/2019 : I watched a video about ethology https://www.youtube.com/watch?v=BvLihzeQzGk.

03/11/2019 : I watched a video about stress management https://www.youtube.com/watch?v=2vhIGYKW4gY and I read the sixth chapter of "The Hobbit".
